A publishing infrastructure for AI-assisted academic authoring

### 2023-12-26 latex/manuscript.tex
latex: add competing interests statement
latex: add data availability statement

@@

>>>>

The University of Colorado filed the U.S. Provisional Patent Application for the "Publishing Infrastructure For AI-Assisted Academic Authoring" invention with the U.S. Patent and Trademark Office.
The authors of this article, Milton Pividori and Casey Greene, are the inventors in this patent.

@@

The manuscripts' text used for evaluation in this article are available in their GitHub repositories, at \url{https://github.com/greenelab/ccc-manuscript}, \url{https://github.com/greenelab/phenoplier_manuscript} and \url{https://github.com/greenelab/manubot-gpt-manuscript}.
The source code of the Manubot AI Editor is available in GitHub, at \url{https://github.com/manubot/manubot-ai-editor}.
